null_model

### 2020-06-09 analysis/ts_null_model.Rmd
Function to get sample occurrences for all studies and plots.

  species_pool <- data %>% 
    filter(study_id == study, plot == plot_id) %>%
    pull(id) %>%
    unique() #get column of unique scientific names

@@

  site_samples <- data.frame()
  for (j in 1:n){
    iter_samples <- data.frame()
    for(i in rich_levels){
    iter_samples <- rbind(iter_samples, get_samp_species(i))
    }
    site_samples <- rbind(site_samples, iter_samples %>% mutate(n = j))
  }
  site_samples %>%
    mutate(study_id = study, plot = plot_id, value = 1) %>%
    spread(samp_species, value)
 # return(site_samples %>% mutate(study_id = study, plot = plot_id))
}

@@

get_sample_FD <- function(data, n){
  #get random sample for each region and richness level
  plots <- data %>%
    select(site_id, plot) %>%
    distinct()

  sample_occurrence <- pmap_dfr(plots[1:10,], get_plot_sample)

  sample_species_mat <- select(sample_occurrence, -richness, -site_id) %>% #want only species x site info
    select(sort(current_vars())) #sort columns to be in alphabetical order, required for dbFDI()
  sample_trait_mat <- clean_trait_matrix(get_trait_matrix(colnames(sample_species_mat)))

  sample_fd <- as.data.frame(dbFD_joggle(x = sample_trait_mat, a = sample_species_mat, w.abun = FALSE))

  df <- sample_occurrence %>%
    select(region, richness) %>%
    bind_cols(sample_fd) %>%
    mutate(merge_test = case_when(
      richness == nbsp ~ TRUE,
      TRUE ~ FALSE
    ))

  if(sum(df$merge_test) != dim(df)[1]) warning("richness and region columns may not have been appropriately joined with FD data")

  path <- paste0(here(), "/data/fd_site_samples/", x, "_tmp.tsv.bz2")
  write_tsv(df, path)
  #pb_upload(path)
}
```

```{r}
n <- 100 #sample size

if(!dir.exists(here::here("data", "fd_site_samples"))){
  dir.create(paste0(here::here(), "/data/fd_site_samples"))
  system.time({out <- future_map(1:n, get_sample_FD)})
}

sim <- purrr::map_dfr(fs::dir_ls(path = here::here("data", "fd_samples"), glob="*.tsv.bz2"), readr::read_tsv, .id = "sample")

>>>>

  species_pool <- data %>% 
    filter(study_id == study, plot == plot_id) %>%
    pull(id) %>%
    na.omit() %>%
    unique() #get column of unique scientific names

@@

  site_samples <- data.frame()
  for (j in 1:n){
    iter_samples <- data.frame()
    for(i in rich_levels){
    iter_samples <- rbind(iter_samples, get_samp_species(i))
    }
    site_samples <- rbind(site_samples, iter_samples %>% mutate(n = j))
  }
  site_samples %>%
    mutate(study_id = study, plot = plot_id, value = 1) %>%
    pivot_wider(names_from = samp_species, values_from = value, values_fill = list(value = 0))
}

@@

get_trait_matrix <- function(species_list, trait_list){ 
  traits <- biotime_traits %>%
    filter(id %in% species_list) %>%
    dplyr::select(id, all_of(trait_list)) %>%
    distinct() %>%
    arrange(id) %>%
    column_to_rownames(var = "id")
}
```

Get dataframe of samples for each plot and corresponding species and trait matrices
```{r}
n = 100

plots <- biotime_traits %>%
    select(study = study_id, plot_id = plot) %>%
    distinct()

sample_occurrence <- pmap_dfr(plots[1:10,], get_plot_sample, data = biotime_traits, n = n) %>%
  replace(is.na(.), 0)

sample_species_mat <- select(sample_occurrence, -c(richness, study_id, plot, n)) %>% #want only species x site info
  select(sort(tidyselect::peek_vars())) #sort columns to be in alphabetical order, required for dbFDI()

traits <- colnames(biotime_traits)[17:64]
sample_trait_mat <- clean_trait_matrix(get_trait_matrix(colnames(sample_species_mat), traits))
```

Explore different functional diversity approaches, starting with original FD application

```{r}
library(FD)

#get diversity metrics from FD package
sample_fd <- as.data.frame(dbFD(x = sample_trait_mat, a = sample_species_mat, w.abun = FALSE))

 #checks for merging output with richness/study info
df <- sample_occurrence %>%
  select(richness, study_id, plot, n) %>%
  bind_cols(sample_fd) %>%
  mutate(merge_test = case_when(richness == nbsp ~ TRUE,
                                TRUE ~ FALSE))

if (sum(df$merge_test) != dim(df)[1])
  warning("richness and region columns may not have been appropriately joined with FD data")
```

BAT
```{r}
library(BAT)
